---
title: "resido_white_lupin_example"
output: html_document
date: "`r Sys.Date()`"


---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Percent sulfur amino acids of all white lupin sequences

```{r percent, include=FALSE}
lupin_protein_dataframe <- resido::resido_amino_acid_group_percent("~/resido/sample_data/white_lupin_proteins.FASTA", "sulfur", sort_by = "percent_amino_acid_group", decreasing = TRUE)
```

## Show the first ten rows of the "percent" output
```{r subset_dataframe, include=TRUE}
lupin_dataframe_top_ten <- lupin_protein_dataframe[1:10, , drop = FALSE]
```

## Create a new fasta file with the top ten highest sulfur sequences

```{r dataframe_to_fasta, include=TRUE}
resido::write.df_to_fasta(lupin_dataframe_top_ten, output_dir = "~/resido/sample_data")
```

## All amino acid frequencies of the top ten highest sulfur amino acid sequences

```{r all_aa, include=TRUE}
resido::all_amino_acids_dataframe("~/resido/sample_data/lupin_dataframe_top_ten.fasta")
```

## Heat map of top ten most sulfur white lupin sequences

```{r heatmap, include=TRUE}
resido::create_aa_heatmap("~/resido/sample_data/lupin_dataframe_top_ten.fasta")
```

## plot of amino acid frequency of the top sulfur sequence

```{r freq_plot, include=TRUE}
resido::plot_amino_acid_frequency("MQCYAMLCGAMQCDGMLCDAMLCDAMRCYAKRCDAIICYSMLCYSMLCYSMRCYAMRCYAMQCDVMQCYAM")
```

## calculating the max Met aa per 100 residues (top 10 sulfur fasta seq)

```{r max_met_per_100, include=TRUE}
resido::calculate_max_aa_per_100("~/resido/sample_data/lupin_dataframe_top_ten.fasta", "M")
```

## calculating the max Cys aa per 100 residues (top 10 sulfur fasta seq)

```{r max_cys_per_100, include=TRUE}
resido::calculate_max_aa_per_100("~/resido/sample_data/lupin_dataframe_top_ten.fasta", "C")
```
